### 2024-06-17 basic-statistics.qmd
20240616 - number and cross-reference equations

Below is conditional probability notation for a left-tailed directional test (i.e., Quarterbacks have <u>shorter</u> careers than Running Backs; or number of carries is <u>negatively</u> associated with injury likelihood):

$$
p\text{-value} = Pr(T \le t | H_0)
$$

@@

Below is conditional probability notation for a right-tailed directional test (i.e., Quarterbacks have <u>longer</u> careers than Running Backs; or number of carries is <u>positively</u> associated with injury likelihood):

$$
p\text{-value} = Pr(T \ge t | H_0)
$$

Below is conditional probability notation for a two-tailed non-directional test (i.e., Quarterbacks <u>differ</u> in the length of their careers compared to Running Backs; or number of carries is <u>associated</u> with injury likelihood):

$$
p\text{-value} = 2 \times \text{min}(Pr(T \le t | H_0), Pr(T \ge t | H_0))
$$

@@

If the distribution of the test statistic is symmetric around zero, the *p*-value for the two-tailed non-directional test simplifies to:

$$
p\text{-value} = 2 \times Pr(T \ge |t| | H_0)
$$

>>>>

The conditional probability notation for a left-tailed directional test (i.e., Quarterbacks have <u>shorter</u> careers than Running Backs; or number of carries is <u>negatively</u> associated with injury likelihood) is in @eq-pvalueLeftTailed.

$$
p\text{-value} = Pr(T \le t | H_0)
$$ {#eq-pvalueLeftTailed}

@@

The conditional probability notation for a right-tailed directional test (i.e., Quarterbacks have <u>longer</u> careers than Running Backs; or number of carries is <u>positively</u> associated with injury likelihood) is in @eq-pvalueRightTailed.

$$
p\text{-value} = Pr(T \ge t | H_0)
$$ {#eq-pvalueRightTailed}

The conditional probability notation for a two-tailed non-directional test (i.e., Quarterbacks <u>differ</u> in the length of their careers compared to Running Backs; or number of carries is <u>associated</u> with injury likelihood) is in @eq-pvalueTwoTailed.

$$
p\text{-value} = 2 \times \text{min}(Pr(T \le t | H_0), Pr(T \ge t | H_0))
$$ {#eq-pvalueTwoTailed}

@@

If the distribution of the test statistic is symmetric around zero, the *p*-value for the two-tailed non-directional test simplifies to @eq-pvalueTwoTailedSimple.

$$
p\text{-value} = 2 \times Pr(T \ge |t| | H_0)
$$ {#eq-pvalueTwoTailedSimple}

### 2024-06-17 player-evaluation.qmd
20240613 - fix typo
20240616 - number and cross-reference equations

In terms of consistency, how consistent was the player they from game to game and from season to season?
For instance, we could examine the standard deviations of players' fantasy points across games in a given season.
However, the standard deviation tends to be upwardly biased as the mean increases.
So, we can account for the player's mean fantasy points per game by dividing their game-to-game standard deviation of fantasy points ($\sigma$) by their mean fantasy points across games ($\mu$).
This is known as the coefficient of variation (CV):

$$
CV = \frac{\sigma}{\mu}
$$

@@

playerA_cv <- playerA_mean / playerA_sd
playerB_cv <- playerB_mean / playerb_sd
```

>>>>

In terms of consistency, how consistent was the player they from game to game and from season to season?
For instance, we could examine the standard deviations of players' fantasy points across games in a given season.
However, the standard deviation tends to be upwardly biased as the mean increases.
So, we can account for the player's mean fantasy points per game by dividing their game-to-game standard deviation of fantasy points ($\sigma$) by their mean fantasy points across games ($\mu$).
This is known as the coefficient of variation (CV), which is provided in @eq-coefficientOfVariation.

$$
CV = \frac{\sigma}{\mu}
$$ {#eq-coefficientOfVariation}

@@

playerA_cv <- playerA_mean / playerA_sd
playerB_cv <- playerB_mean / playerB_sd
```
